`tidyfun`

### 2019-12-31 papers.Rmd
fix link to CV, minor updates elsewhere

>>>>

E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
<i> Environmental Health, </i> 
<b>18</b> ???.
[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]

### 2019-12-31 research.Rmd
updating subpage stylesheets so academicons work throughout
fix link to CV, minor updates elsewhere

<link rel="stylesheet" href="styles.css" type="text/css" />
<br>

@@

<img src="images/accel_covariate.jpg" alt="kinematics" style="width:80%; border:5px solid">

>>>>

<link rel="stylesheet" href="styles.css" type="text/css" />
<link rel="stylesheet" href="academicons/css/academicons.min.css"/>

<br>

@@

<img src="images/accel_covariate.jpg" alt="accel" style="width:80%; border:5px solid">

### 2019-12-31 tidyfun.Rmd
fix link to CV, minor updates elsewhere

The code in this page is drawn from [`tidyfun`](https://fabian-s.github.io/tidyfun/) vignettes, and is intended as a quick introduction; for more details, please read the complete documentation!

@@

```{r, eval = FALSE}
devtools::install_github("fabian-s/tidyfun")
```

>>>>

The code in this page is drawn from [`tidyfun`](https://tidyfun.github.io/tidyfun/) vignettes, and is intended as a quick introduction; for more details, please read the complete documentation!

@@

```{r, eval = FALSE}
devtools::install_github("tidyfun/tidyfun")
```
